MSOA domestic Electricity and Gas maps

### 2021-08-26 MSOA domestic Elec and Gas.Rmd
Adding in Histograms

####Mapping the change from 2010 to 2019
```{r Creating the difference in MSOA mean dom elec consumption variable}
domelec_MSOA_2010<-readr::read_csv(paste0(dataFolder,"energy/electricity/MSOA Dom Elec csv/MSOA_DOM_ELEC_2010.csv"),skip = 1)
domelec_MSOA_2019<-readr::read_csv(paste0(dataFolder, "energy/electricity/MSOA Dom Elec csv/MSOA_DOM_ELEC_2019.csv"))
domelec_MSOA_2010$domelec2010<-domelec_MSOA_2010$'Mean consumption (kWh per meter)'
domelec_MSOA_2019$domelec2019<-domelec_MSOA_2019$'Mean consumption (kWh per meter)'
merged_domelec<-merge(domelec_MSOA_2010, domelec_MSOA_2019, by="Middle Layer Super Output Area (MSOA) Code", all=TRUE)
names(merged_domelec)
merged_domelec$domelec_diff<-merged_domelec$domelec2019 - merged_domelec$domelec2010
summary(merged_domelec)
```
```{r Mapping the MSOA difference in mean dom elec consumption}
merged_domelec$MSOA11CD<-merged_domelec$"Middle Layer Super Output Area (MSOA) Code"
msoa_domelec20102019<-merge(msoa_sf_data, merged_domelec)
ggplot2::ggplot(msoa_domelec20102019)+geom_sf(aes(fill=domelec_diff))+scale_fill_continuous(name="Change in Mean comsumpton (kWh per meter)",low="green",high="red")+labs(caption="Solent(all MSOAs)")
```
####Map with Overlay
```{r Check leaflet for Change in dom elec consumption}
library(leaflet)

@@

```{r Mapping the change in dom mean gas comsumption}
merged_domgas$MSOA11CD <- merged_domgas$"Middle Layer Super Output Area (MSOA) Code" #creating a variable with the LSOA code in the same name as in sf_data
msoa_domgas20102019 <- merge(msoa_sf_data, merged_domgas) #merging these
ggplot2::ggplot(msoa_domgas20102019) +
  geom_sf(aes(fill=mc_diff))+ 
  scale_fill_continuous(name="Change in Gas: Mean kWh per meter", low="green",high="red")+
  labs(caption ="Solent (all MSOAs)")
```

>>>>

####Mapping the change from 2010 to 2019
```{r Creating the difference in MSOA mean dom elec consumption variable}
domelec_MSOA_2010<-readr::read_csv(paste0(dataFolder,"energy/electricity/MSOA Dom Elec csv/MSOA_DOM_ELEC_2010.csv"),skip = 1)
domelec_MSOA_2019<-readr::read_csv(paste0(dataFolder, "energy/electricity/MSOA Dom Elec csv/MSOA_DOM_ELEC_2019.csv"))
domelec_MSOA_2010$domelec2010<-domelec_MSOA_2010$'Mean consumption (kWh per meter)'
domelec_MSOA_2019$domelec2019<-domelec_MSOA_2019$'Mean consumption (kWh per meter)'
merged_domelec<-merge(domelec_MSOA_2010, domelec_MSOA_2019, by="Middle Layer Super Output Area (MSOA) Code", all=TRUE)
names(merged_domelec)
merged_domelec$domelec_diff<-merged_domelec$domelec2019 - merged_domelec$domelec2010
summary(merged_domelec)
```
```{r Mapping the MSOA difference in mean dom elec consumption}
merged_domelec$MSOA11CD<-merged_domelec$"Middle Layer Super Output Area (MSOA) Code"
msoa_domelec20102019<-merge(msoa_sf_data, merged_domelec)
ggplot2::ggplot(msoa_domelec20102019)+geom_sf(aes(fill=domelec_diff))+scale_fill_continuous(name="Change in Mean comsumpton (kWh per meter)",low="green",high="red")+labs(caption="Solent(all MSOAs)")

#Histogram
msoa_domelec20102019$pc_diff <- 100* (msoa_domelec20102019$domelec_diff/msoa_domelec20102019$domelec2010)
t_diff <-dplyr::select(as.data.frame(msoa_domelec20102019), MSOA11CD, 'Middle Layer Super Output Area (MSOA) Code',domelec2010, domelec2019, domelec_diff, pc_diff)
head(arrange(t_diff, pc_diff))
head(arrange(t_diff, -pc_diff))
ggplot2::ggplot(t_diff, aes(x=pc_diff)) +
  geom_histogram()
```
####Map with Overlay
```{r Check leaflet for Change in dom elec consumption}
library(leaflet)

@@

```{r Mapping the change in dom mean gas comsumption}
merged_domgas$MSOA11CD <- merged_domgas$"Middle Layer Super Output Area (MSOA) Code" #creating a variable with the LSOA code in the same name as in sf_data
msoa_domgas20102019 <- merge(msoa_sf_data, merged_domgas) #merging these
ggplot2::ggplot(msoa_domgas20102019) +
  geom_sf(aes(fill=mc_diff))+ 
  scale_fill_continuous(name="Change in Gas: Mean kWh per meter", low="green",high="red")+
  labs(caption ="Solent (all MSOAs)")

#Histogram
msoa_domgas20102019$pc_diff <- 100* (msoa_domgas20102019$mc_diff/msoa_domgas20102019$domgas2010)
t_diff <- dplyr::select(as.data.frame(msoa_domgas20102019), MSOA11CD, 'Middle Layer Super Output Area (MSOA) Code',domgas2010, domgas2019, mc_diff, pc_diff)
head(arrange(t_diff, pc_diff))
head(arrange(t_diff, -pc_diff))
ggplot2::ggplot(t_diff, aes(x=pc_diff)) +
  geom_histogram()
